Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2012-03-08 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2012:03:08	16:38:22	(Thu 8.Mar)
la2pdf commit - 2012:03:08	17:11:31	(Thu 8.Mar)
la2pdf commit - 2012:03:08	17:44:40	(Thu 8.Mar)
la2pdf commit - 2012:03:08	20:59:03	(Thu 8.Mar)
la2pdf commit - 2012:03:08	22:55:01	(Thu 8.Mar)

@@

\begin{itemize}
\item Sell it!
\item As briefly as possible, introduce beamforming.
\item Adaptive beamformer potential
\item Why adaptive beamformers struggle in active sonar systems. Correlated noise, robustification kills the adaptive potential. Quite computationally intensive. Constraints must be applied in one way or another - parameters must be tuned.
\item LCA is like DAS, only we test several windows and choose the one that yield the lowest beamformer output power. Ultrasound \cite{Synnevag2008}, active sonar \cite{Buskenes2011}\cite{Blomberg2011}\cite{Blomberg2012}\todo{who was that guy in the 80ties?}
\item Outline: 
\begin{itemize}
\item Methods.
\item See what happens to Capon's response when means for robustification are added.
\item Setup the window set for LCA to match this.
\item Notice that the LCA performs like Capon, even with a small window database.
\item Start with Kaiser, see that other window functions also work well.
\end{itemize}
\end{itemize}

@@

Minimum variance distortionless resonse
\begin{align}
\underset{\w[n]}{\argmin}\, E\{ |z[n]|^2 \} = \underset{\w[n]}{\argmin}\, \w\H[n]\R[n]\w[n], 
\end{align}
subject to
\begin{align}
\w\H[n]\a = 1,
\end{align}
where
\begin{align}
\R[n] = E\{ \x\x\H \}.
\end{align}s<
If $\eR$ is the estimate of $\R$, the solution to the MVDR beamformer is
\begin{gather*}
\vec w[n] = \frac{\hat{\mat R}\,\!^{-1}[n]\vec a}{\vec a\H\hat{\mat R}\,\!^{-1}[n]\vec a} = \frac{\text{\raisebox{1.9pt}{$\vec\chi$}}[n]}{\vec a\H\text{\raisebox{1.9pt}{$\vec\chi$}}[n]}
\end{gather*}
A robust estimate of $\eR$ is found by
\begin{itemize}
\item Spatial averaging to decorrelate noise from signal. \emph{Subarray averaging} used here.
\item Temporal averaging to ensure valid speckle statistics.
\item \emph{Diagonal loading} to ensure  numerical stability prior to inversion.
\item Choice of robustification parameters (C-I) \cite{}
\end{itemize}

@@

>>>>

% \RequirePackage[utf8]{inputenc}%              % Set input encoding (optionally latin1)
% \RequirePackage[T1]{fontenc}%                 % Set font encoding

@@

\begin{itemize}
\item Sell it!
\item As briefly as possible, introduce beamforming.
\item Adaptive beamformer's potential lies in its ability to suppress interference power
\item Why adaptive beamformers struggle in active sonar systems. Correlated noise, robustification kills the adaptive potential. Quite computationally intensive. Constraints must be applied in one way or another - parameters must be tuned.
\begin{itemize}
\item Increases variance of speckle, spatial compunting needed \cite{Vignon2009}. Subarray averaging applied here \cite{Synnevag2007}
\end{itemize}
\item LCA is like DAS, only we test several windows and choose the one that yield the lowest beamformer output power. Ultrasound \cite{Synnevag2008}, active sonar \cite{Buskenes2011}\cite{Blomberg2011}\cite{Blomberg2012}\todo{who was that guy in the 80ties?}
\item Outline: 
\begin{itemize}
\item Methods.
\item See what happens to Capon's response %\cite{Synnevag2007}  when means for robustification are added.
\item Setup the window set for LCA to match this.
\item Notice that the LCA performs like Capon, even with a small window database.
\item Start with Kaiser, see that other window functions also work well.
\end{itemize}
\end{itemize}

@@

Minimum variance distortionless resonse \cite{Capon1969}
\begin{align}
\underset{\w[n]}{\argmin}\, E\{ |z[n]|^2 \} = \underset{\w[n]}{\argmin}\, \w\H[n]\R[n]\w[n], 
\end{align}
subject to
\begin{align}
\w\H[n]\a = 1,
\end{align}
where
\begin{align}
\R[n] = E\{ \x\x\H \}.
\end{align}s<
If $\eR$ is the estimate of $\R$, the solution to the MVDR beamformer is
\begin{gather*}
\vec w[n] = \frac{\hat{\mat R}\,\!^{-1}[n]\vec a}{\vec a\H\hat{\mat R}\,\!^{-1}[n]\vec a} = \frac{\text{\raisebox{1.9pt}{$\vec\chi$}}[n]}{\vec a\H\text{\raisebox{1.9pt}{$\vec\chi$}}[n]}
\end{gather*}
A robust estimate of $\eR$ is found by
\begin{itemize}
\item Spatial averaging to decorrelate noise from signal. \emph{Subarray averaging} used here.
\item Temporal averaging to ensure valid speckle statistics.
\item \emph{Diagonal loading} to ensure  numerical stability prior to inversion.
\item Choice of robustification parameters \cite{Synnevag2007}
\end{itemize}

@@

\begin{figure}[!t]\centering
% \includegraphics[width=2.5in]{}
\caption{Simulation Results}
\label{fig_sim}
\end{figure}
